\textbf{Computational Fuzzy Extractors}

### 2013-03-07 CompFuzzExt.tex
Adding statement of theorem from micciancio and peikert

\section{Preliminaries}
\label{sec:preliminaries}
For a random variable $X = X_1,..., X_n$ where each $X_i$ is over some $\chi$, we denote by $X_{1,..., k} = X_1,..., X_k$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$, 
%the {\em (worst-case) conditional min-entropy} of $X$ given $Y$ is  $\Hoo(X|Y) = -\log(\max_{x,y} \Pr[X=x|Y=y])$, and
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.  
%The {\em collision probability} of  $X$ is 
%$\col(X) = \sum_{x} \Pr[X=x]^2$.
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$. We write $X \approx_{\epsilon} Y$ if $\Delta(X,Y) \leq \epsilon$, and when $\epsilon$ is negligible (in the appropriate parameter, as clear from the context) then we say $X$ and $Y$ are \emph{statistically close}.  For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.  We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.
For a metric space $(\mathcal{M}, \dis)$ be define the \emph{(closed) ball of radius $t$ around $x$} as the  set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$. $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.

@@

We review definitions of Shannon codes~\cite{shannon1949mathematical}:
\begin{definition}
Let $\mathcal{C}$ be a set over space $\mathcal{M}$.  We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\sample(c, t')) \neq c]<\epsilon$. To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
\end{definition}
This is a slightly stronger formulation than usual, in that we require the code to correct random errors of every size $t'<t$. \footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compare to the volume of the ball of size $t$.  For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.  However, we work with an arbitrary recover functionality that is not necessarily monotone.}.

Shannon codes work for all codewords. We can also consider a formulation that works for an ``average'' codeword. \begin{definition}
Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
$\Pr_{c\leftarrow C}[\rec(\sample(c, t')) \neq c]<\epsilon$.
\end{definition}
An average error Shannon code is convertible to a maximal error Shannon code with a small loss.  We use the following pruning argument from Cover and Thomas~\cite[Pages 202-204]{cover2006elements} (we provide a proof in \secref{sec:proof of average to maximal error}):
\begin{lemma}
\label{lem:averageToMaximalError}
Let $C$ be a distribution with $\Hoo(C)\geq k$ and let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$.  There is a set $C'$ with $|C'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
\end{lemma}

We are now ready to show our main result: HILL-entropy secure sketches imply maximal-error Shannon codes~(proof in \secref{sec:proof of thm sketch implies code}).
\begin{theorem}\label{thm:impSketchArbitraryW}
Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  Assume $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$, where $s_{rec}$ is the circuit size of $\rec$.  Then there exists $x$ and a set $C$ with $|C'|\geq 2^{\tilde{m}-2}$ that is a $(t, 4(\epsilon+\delta))$-Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
%Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.  If $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $O(s_{neigh}+s_{rec})$, then $\exists x, W'$ where $|W'|\geq |W|/2 \geq 2^{k-1}$ such that $W'$ is a $(t, 2\epsilon)$ Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
\end{theorem}
%The code provided in \thref{thm:impSketchArbitraryW} is weaker than a Shannon error correcting code~\cite{shannon1948}.  In a Shannon code, for all codewords $c, \Pr[c'\leftarrow \sample(c) \wedge \rec(c') \neq c]<\epsilon$.  Bounds for this type of code are well known~\cite{shannon1948} and efficient constructions exist~\cite{forney1966}.  Requiring proper decoding for only a random codeword is a significant restriction particularly in the case where the probability of outcomes in $W$ differs significantly~(e.g. where $\exists w_1,w_2\in W$ such that $\Pr[W=w_1]/\Pr[W=w_2] = \ngl$).  However, this is still a meaningful set of error correcting codes.  A similar question is considered in Appendix C of \cite{DBLP:journals/siamcomp/DodisORS08}.  They are able to achieve results for Hamming codes~(as they are not restricted to sampling a polynomial portion of the space)\bnote{expand on this explanation}.

It is known (see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein) that, for the Hamming metric, any Shannon code (in the stronger sense defined by us) can be converted into an information-theoretic secure sketch.  The idea is to use the code offset construction, but randomize the order of the bits of $w$ first, via  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$). The formal statement is in the following Lemma.
\begin{lemma}
\label{lem:shannon to sketch}
For an alphabet $Z$, let $\mathcal{C}$ over $Z^n$ be a $(t, \delta)$ Shannon code.  % with recovery procedure $\rec'$.
%  Let $W$ be a distribution with $\Hoo(W)\geq k$. 
%
% Define the following procedures
%\lnote{I think this description is buggy}
%\begin{center}
%\begin{tabular}{c|c}
%\begin{minipage}{3in}
%\textbf{\sketch}
%\begin{enumerate}
%\item Input $w\leftarrow W$.
%\item Sample $\pi$ from the space of all permutations from $\pi: [n]\rightarrow [n]$.
%\item Sample $c\leftarrow \mathcal{C}$.
%\item Apply $\pi$ bitwise to get $x_i = w_{\pi(i)}$.
%\item Output $p = x \oplus c, \pi$.
%\end{enumerate}
% \end{minipage} &
%\begin{minipage}{3in}
%\textbf{\rec}
%\begin{enumerate}
%\item Input $(w', p, \pi)$
%\item Apply $\pi^{-1}$ bitwise to get $x_i' = w_{\pi(i)}$.
%\item Compute $c' = p \oplus x'$.
%\item Compute $c = \rec'(c)$.
%\item Output $p\oplus c$.
%\\
%\end{enumerate}
%\end{minipage} 
%\end{tabular}
%\end{center}
Then there exists a $(Z^n, m, m-(n\log|Z|-\log |\mathcal{C}|), t)$ secure sketch with error $\delta$ for the Hamming metric over $Z^n$. 
%satisfies the following properties~(probability over the choice of $\pi$ in $\sketch$):
%\begin{itemize}
%\item Correctness: $\forall w, w'$ where $dis(w, w')\leq t$, $\Pr[\rec(w', \sketch(w))\neq w]<\epsilon$.
%\item Security: $\Hav(W |\sketch(W)) \geq \Hoo(W) - (n-\log |C|)$.
%\item Efficiency: $\sketch$ is efficient if sampling from $C$ is efficient and $\rec$ is efficient if $\rec'$ is efficient.
%\end{itemize}
\end{lemma}
%\begin{construction}
%Let $\delta >0$ be a parameter.
%Let $C$ be a $(t, \epsilon)$ Shannon code over $\{0,1\}^n$.  Choose a permutation $\pi:\mathcal{M}rightarrow \mathcal{M}$ that is $\beta$-almost independent $\ell = \delta n/\log(n)$-wise permutation.  Thefn for $\beta = 2^{-\ell}
%\end{construction}
Putting together \thref{thm:impSketchArbitraryW} and \lemref{lem:shannon to sketch} gives us the negative result for the Hamming metric: a HILL-entropy secure sketch (for the uniform distribution) implies an information-theoretic one with similar parameters:
\begin{corollary}
\label{cor:rec yields sketch}
Let $Z$ be an alphabet. Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(Z^n, n\log |Z|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $Z^n$, with $\rec'$ of circuit size $s_{rec}$.
If $s_{sec}=\Omega(t(s_{rec} + n))$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
$4(\epsilon+\delta)$. 
%Let $(\mathcal{M}, d)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  If no $(t, \epsilon)$-average error Shannon code over $\mathcal{M}$ exists of size $2^k$ then, $\forall (s_{rec}, t)$ recovery procedures $(\sketch, \rec)$ $H^{\hill}_{\epsilon, s}(X|\sketch(X))\not\geq k$ for $s=O(s_{rec}+s_{neigh})$.
\end{corollary}
\textbf{Notes:} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.

@@

\begin{definition}~\cite[Definition 7]{DBLP:conf/eurocrypt/HsiaoLR07}
\label{def:unp entropy}
For a distribution $(X, Z)$, we say that $X$ has \emph{unpredictability entropy} at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\delta^{\mathcal{D}_{s_{sec}}}((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
\[
\Pr[C(Z) = Y ] \leq 2^{-k}
.\]
\end{definition}
We will say a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy}$(\mathcal{M}, m, \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-hard with error $\delta$ if it satisfied \defref{def:secure sketch} with the security requirement replaces with $H^{\unp}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.  
We consider this notion to be a natural notion for a computational sketch as it can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}):
\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
\label{lem:unp extraction} 
Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.  Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
\end{lemma}
Thus, using a sketch that retained unpredictability entropy and a reconstructive extractor we could build a computational fuzzy extractor~(in a similar fashion to \lemref{lem:fuzzy ext construction}).

Unfortunately, unpredictability entropy must also depend on $t$.  An adversaries ability to predict the output of the \rec algorithm increases with as $t$ grows.  %That is, $\forall Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)) , (Y, \sketch(W))$ our ability to predict $Y$ increases as $|B_t(\cdot)|$ increases.  
The formal statement is below:
\begin{theorem}
\label{thm:imp of unp entropy}
Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be an Unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  If $s_{sec} = \Omega(|\rec|+b)$, then $\tilde{m}\leq b - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
\end{theorem}
This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.  The main difference with \thref{thm:impSketchArbitraryW} is that it is unknown if the indistinguishable distribution contains many points.  This means we cannot construct a good code out of the points of $Y$.  In \secref{sec:proof of imp unp entropy}, we prove a stronger version of \thref{thm:imp of unp entropy}, based on a relaxed notion of unpredictability entropy.%Our bound is a result of the Hamming bound for the space.

@@

The lower bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} are strongest for high entropy sources.  The results get weaker as we consider sources with lower starter entropy.  This is necessary, if a source contains only codewords (of an error correcting code), no sketch is necessary.  This means we cannot rule out computational sketches for other arbitrary lower entropy distributions.

Both of the lower bound results arise because the reduction can ensure that \rec functions as an error-correcting code for many points of the output distribution.  It may be possible to avoid this problem if \rec outputs a fresh random variable\footnote{If some efficient algorithm can take the output of $\rec$ and efficiently transform it back to the source $W$, the bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} both apply.  This means that we need to consider constructions that are hard to invert~(either information-theoretically or computationally).}.  An algorithm that outputs a fresh random variable would be a computational fuzzy conductor~(see~\cite{KanukurthiR09} for the definition of a fuzzy conductor).  Our construction~(in \secref{sec:fuzzyCompExt}) has pseudorandom output and immediately satisfies definition of a computational fuzzy extractor~(\defref{def:comp fuzzy extractor}).  It is unknown if a more efficient construction could be achieved using a computational fuzzy conductor that is not also a computational fuzzy extractor.
\bnote{Not happy with this wording, revise}

@@

In this section we describe our main construction.  Our construction uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.   Let $\mathcal{I}_t$ be an algorithm that decodes a random linear code with at most $t$ errors~(not necessarily efficient).  We provide an informal description below.
%Please refer to \consref{cons:informal construction} for the description of the construction.

>>>>

\section{Preliminaries}
\label{sec:preliminaries}
For a random variable $X = X_1||...|| X_n$ where each $X_i$ is over some alphabet $Z$, we denote by $X_{1,..., k} = X_1||...|| X_k$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$, 
%the {\em (worst-case) conditional min-entropy} of $X$ given $Y$ is  $\Hoo(X|Y) = -\log(\max_{x,y} \Pr[X=x|Y=y])$, and
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.  
%The {\em collision probability} of  $X$ is 
%$\col(X) = \sum_{x} \Pr[X=x]^2$.
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$. %We write $X \approx_{\epsilon} Y$ if $\Delta(X,Y) \leq \epsilon$, and when $\epsilon$ is negligible (in the appropriate parameter, as clear from the context) then we say $X$ and $Y$ are \emph{statistically close}.  
For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.  We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.
For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.  If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t(\cdot)|$ the size of a ball of radius $t$.  For the Hamming metric over $Z^n$ the size of $B_t(\cdot) = \sum_{i=0}^t {n \choose t} (|Z|-1)^i $, for clarity we express this value as $B_t(\cdot)$.  $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
During the presentation, we denote bold letters to be vectors or matrix, capitalized letters to be random variables, and lower case letter to be the elements in the vector.

@@

We review definitions of Shannon codes~\cite{shannon1949mathematical}:
\begin{definition}
Let $\mathcal{C}$ be a set over space $\mathcal{M}$.  We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\sample(c, t')) \neq c]<\epsilon$. To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
\end{definition}
This is a slightly stronger formulation than usual, in that we require the code to correct random errors of every size $t'<t$\footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compare to the volume of the ball of size $t$.  For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.  However, we work with an arbitrary recover functionality that is not necessarily monotone.}.

Shannon codes work for all codewords. We can also consider a formulation that works for an ``average'' codeword. \begin{definition}
Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
$\Pr_{c\leftarrow C}[\rec(\sample(c, t')) \neq c]<\epsilon$.
\end{definition}
An average error Shannon code is convertible to a maximal error Shannon code with a small loss.  We use the following pruning argument from Cover and Thomas~\cite[Pages 202-204]{cover2006elements} (we provide a proof in \secref{sec:proof of average to maximal error}):
\begin{lemma}
\label{lem:averageToMaximalError}
Let $C$ be a distribution over space $\mathcal{M}$ with $\Hoo(C)\geq k$ and let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$.  There is a set $C'$ with $|C'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
\end{lemma}

We can now formalize the intuition above.  A sketch that retains $\tilde{m}$-bits of HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in \secref{sec:proof of thm sketch implies code}).
\begin{theorem}\label{thm:impSketchArbitraryW}
Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  Assume $s_{sec}= \Omega(t(s_{neigh}+s_{rec}))$, where $s_{rec}$ is the circuit size of $\rec$.  Then there exists a value $s$ and a set $C$ with $|C'|\geq 2^{\tilde{m}-2}$ that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
%Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.  If $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $O(s_{neigh}+s_{rec})$, then $\exists x, W'$ where $|W'|\geq |W|/2 \geq 2^{k-1}$ such that $W'$ is a $(t, 2\epsilon)$ Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
\end{theorem}
%The code provided in \thref{thm:impSketchArbitraryW} is weaker than a Shannon error correcting code~\cite{shannon1948}.  In a Shannon code, for all codewords $c, \Pr[c'\leftarrow \sample(c) \wedge \rec(c') \neq c]<\epsilon$.  Bounds for this type of code are well known~\cite{shannon1948} and efficient constructions exist~\cite{forney1966}.  Requiring proper decoding for only a random codeword is a significant restriction particularly in the case where the probability of outcomes in $W$ differs significantly~(e.g. where $\exists w_1,w_2\in W$ such that $\Pr[W=w_1]/\Pr[W=w_2] = \ngl$).  However, this is still a meaningful set of error correcting codes.  A similar question is considered in Appendix C of \cite{DBLP:journals/siamcomp/DodisORS08}.  They are able to achieve results for Hamming codes~(as they are not restricted to sampling a polynomial portion of the space)\bnote{expand on this explanation}.

%It is known (see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein) that, 
For the Hamming metric, any Shannon code (in the stronger sense defined by us) can be converted into an information-theoretic secure sketch~(see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein).  The idea is to use the code offset construction, but randomize the order of the bits of $w$ first, via  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$). The formal statement is in the following Lemma.
\begin{lemma}
\label{lem:shannon to sketch}
For an alphabet $Z$, let $\mathcal{C}$ over $Z^n$ be a $(t, \delta)$ Shannon code.  % with recovery procedure $\rec'$.
%  Let $W$ be a distribution with $\Hoo(W)\geq k$. 
%
% Define the following procedures
%\lnote{I think this description is buggy}
%\begin{center}
%\begin{tabular}{c|c}
%\begin{minipage}{3in}
%\textbf{\sketch}
%\begin{enumerate}
%\item Input $w\leftarrow W$.
%\item Sample $\pi$ from the space of all permutations from $\pi: [n]\rightarrow [n]$.
%\item Sample $c\leftarrow \mathcal{C}$.
%\item Apply $\pi$ bitwise to get $x_i = w_{\pi(i)}$.
%\item Output $p = x \oplus c, \pi$.
%\end{enumerate}
% \end{minipage} &
%\begin{minipage}{3in}
%\textbf{\rec}
%\begin{enumerate}
%\item Input $(w', p, \pi)$
%\item Apply $\pi^{-1}$ bitwise to get $x_i' = w_{\pi(i)}$.
%\item Compute $c' = p \oplus x'$.
%\item Compute $c = \rec'(c)$.
%\item Output $p\oplus c$.
%\\
%\end{enumerate}
%\end{minipage} 
%\end{tabular}
%\end{center}
Then there exists a $(Z^n, m, m-(n\log|Z|-\log |\mathcal{C}|), t)$ secure sketch with error $\delta$ for the Hamming metric over $Z^n$. 
%satisfies the following properties~(probability over the choice of $\pi$ in $\sketch$):
%\begin{itemize}
%\item Correctness: $\forall w, w'$ where $dis(w, w')\leq t$, $\Pr[\rec(w', \sketch(w))\neq w]<\epsilon$.
%\item Security: $\Hav(W |\sketch(W)) \geq \Hoo(W) - (n-\log |C|)$.
%\item Efficiency: $\sketch$ is efficient if sampling from $C$ is efficient and $\rec$ is efficient if $\rec'$ is efficient.
%\end{itemize}
\end{lemma}
%\begin{construction}
%Let $\delta >0$ be a parameter.
%Let $C$ be a $(t, \epsilon)$ Shannon code over $\{0,1\}^n$.  Choose a permutation $\pi:\mathcal{M}rightarrow \mathcal{M}$ that is $\beta$-almost independent $\ell = \delta n/\log(n)$-wise permutation.  Thefn for $\beta = 2^{-\ell}
%\end{construction}
Putting together \thref{thm:impSketchArbitraryW} and \lemref{lem:shannon to sketch} gives us the negative result for the Hamming metric: a HILL-entropy secure sketch (for the uniform distribution) implies an information-theoretic one with similar parameters:
\begin{corollary}
\label{cor:rec yields sketch}
Let $Z$ be an alphabet. Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(Z^n, n\log |Z|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $Z^n$, with $\rec'$ of circuit size $s_{rec}$.
If $s_{sec}=\Omega(t(s_{rec} + n\log |Z|))$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
$4(\epsilon+t\delta)$. 
%Let $(\mathcal{M}, d)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  If no $(t, \epsilon)$-average error Shannon code over $\mathcal{M}$ exists of size $2^k$ then, $\forall (s_{rec}, t)$ recovery procedures $(\sketch, \rec)$ $H^{\hill}_{\epsilon, s}(X|\sketch(X))\not\geq k$ for $s=O(s_{rec}+s_{neigh})$.
\end{corollary}
\textbf{Notes:} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.

@@

\begin{definition}~\cite[Definition 7]{DBLP:conf/eurocrypt/HsiaoLR07}
\label{def:unp entropy}
For a distribution $(X, Z)$, we say that $X$ has \emph{unpredictability entropy} at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\delta^{\mathcal{D}_{s_{sec}}}((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
\[
\Pr[C(Z) = Y ] \leq 2^{-k}
.\]
\end{definition}
We will say a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch} with the security requirement replaced with $H^{\unp}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.  
We consider this notion to be a natural notion for a computational sketch as it can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}):
\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
\label{lem:unp extraction} 
Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.  Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
\end{lemma}
Thus, if a sketch retained unpredictability entropy we could build a computational fuzzy extractor~(using the construction in \lemref{lem:fuzzy ext construction}).  
Unfortunately, the unpredictability entropy conditioned on the sketch must recreate with $t$.  
%An adversaries ability to predict the output of the \rec algorithm increases with as $t$ grows.  %That is, $\forall Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)) , (Y, \sketch(W))$ our ability to predict $Y$ increases as $|B_t(\cdot)|$ increases.  
The formal statement is below:
\begin{theorem}
\label{thm:imp of unp entropy}
Let $W$ be a distribution over $Z^n$ and let $(\sketch, \rec)$ be an unpredictability-entropy $(Z^n, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  If $s_{sec} = \Omega(|\rec|+n\log |Z|)$, then $\tilde{m}\leq n\log |Z| - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
\end{theorem}
This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.  The main difference with \thref{thm:impSketchArbitraryW} is that it is unknown if the indistinguishable distribution contains many points.  This means we cannot construct a good code out of the points of $Y$.  In \secref{sec:proof of imp unp entropy}, we prove a stronger version of \thref{thm:imp of unp entropy}, based on a relaxed notion of unpredictability entropy.%Our bound is a result of the Hamming bound for the space.

@@

The lower bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} are strongest for high entropy sources.  The results get weaker as we consider sources with lower starter entropy.  This is necessary, if a source contains only codewords (of an error correcting code), no sketch is necessary.  This means we cannot rule out computational sketches for other arbitrary lower entropy distributions.  This same situation occurs when considering lower bounds for information-theoretic sketches.

Both of the lower bound results arise because the reduction can ensure that \rec functions as an error-correcting code for many points of the indistinguishable distribution.  It may be possible to avoid this problem if \rec outputs a fresh random variable\footnote{If some efficient algorithm can take the output of $\rec$ and efficiently transform it back to the source $W$, the bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} both apply.  This means that we need to consider constructions that are hard to invert~(either information-theoretically or computationally).}.  An algorithm that outputs a fresh random variable would be a computational fuzzy conductor~(see~\cite{KanukurthiR09} for the definition of a fuzzy conductor).  Our construction~(in \secref{sec:fuzzyCompExt}) has pseudorandom output and immediately satisfies definition of a computational fuzzy extractor~(\defref{def:comp fuzzy extractor}).  It may be possible to achieve significantly better parameters with a construction that is a computational fuzzy conductor~(but not a computational fuzzy extractor) and then applying an extractor.  We leave this as an open problem.

@@

In this section we describe our main construction.  In this section, we consider only a uniform source $W$, we consider other distributions in \secref{sec:LWE block fixing sources}.  Our construction uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.   Let $\mathcal{I}_t$ be an algorithm that decodes a random linear code with at most $t$ errors.  We provide an informal description below.
%Please refer to \consref{cons:informal construction} for the description of the construction.

\begin{construction}
Let $n$ be a security parameter and let $m> n$.  %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
Define $\gen, \rep$ as follows:%The following construction is a computational secure sketch:
%Code-offset construction of a secure sketch using a random linear code over a finite field $\Fq$. $\mathcal{I}_t (\vA, \vect{D})$ denotes an algorithm that decodes up to $t$ errors, i.e., an algorithm that finds $X'\in \Fq^n$ such that $\vect{A}X'$ is of Hamming distance at most $t$ from $\vect{D}$. $m > n$ are parameters to be figured out later.
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w\leftarrow W$ (where $W$ is some distribution over $\Fq^m$).
\item Sample $\vA\in\Fq^{m\times n}, X\in\Fq^n$ uniformly.
\item Compute $p = (\vA, \vA X+w)$, \\\ $r = X_{1,...,n/2}$.
\item Output $(r, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rec}
\begin{enumerate}
\item \underline{Input}: $(w', p)$ (where the Hamming distance between $w'$ and $w$ is at most $t$).
\item Parse $p$ as $(\vA, \vect{C})$; let $\vect{D}=\vect{C}-w'$.
\item Let $X = \mathcal{I}_t(\vA, \vect{D})$\\
\item Output $r = X_{1,...,n/2}$.
\end{enumerate}
\end{minipage} 
\end{tabular}
\end{center}
\label{cons:informal construction}
\end{construction}

Intuitively, security comes from the computational hardness of decoding random linear codes from a high number of errors (introduced by $w$).  
In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  $\delta^{\mathcal{D}_{s_{sec}}}((X_{1,..., n/2},P), (U_{n/2 \log q}, P))\leq \epsilon$.  Furthermore, this construction is only useful if $\mathcal{I}_t$ can be efficiently implemented.  We demonstrate an efficient $\mathcal{I}_t$ that corrects a super-polynomial number of error patterns in polynomial time.

The rest of this section is devoted to making these intuitive statements precise.
 We describe the \class{LWE} problem and the security of our construction in \secref{subsec:LWE}.
 %a recent variant due to D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} in \secref{subsec:LWE}.  
We describe conditions for efficient decoding in \secref{sec:time main construction}.  In \secref{sec:lossless extractor}, we describe parameter settings where we extract as many bits as the size of our input distribution and thus our construction is lossless.  In \secref{sec:prg based comparison}, we compare \consref{cons:informal construction} to using a information-theoretic fuzzy extractor and running a pseudorandom generator on the output.
